Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-29 paper/section-general-framework.tex
Fix spelling error

\paragraph{Relational interpretation of types.}
We assign a relational interpretation to all well-indexed types $\Delta
\vdash A \isType$ by induction on their derivations, parameterised by
index environments 
$\rho \in \semSort{\Delta}$:
\begin{eqnarray*}
%  \rsem{\Delta \vdash A \isType}M R & : & \semSort\Delta  \to \Rel(\tyPrimSem{A})\\
  \rsem{\tyUnit} \rho & \isDefinedAs & \{(*,*)\} \\
  \rsem{\tyPrim{X}{e_1,\ldots,e_n}}\rho & \isDefinedAs & 
  \semPrimType{\tyPrimNm{X}} (\semIndexExp{e_1}\rho, \ldots,
  \semIndexExp{e_n}\rho)\\
  \rsem{A \tyArr B} \rho & \isDefinedAs & \rsem{A}\rho \relArrow \rsem{B} \rho \\
  \rsem{A \tyProduct B}\rho & \isDefinedAs & \rsem{A} \rho \relTimes \rsem{B} \rho \\
  \rsem{A + B} \rho & \isDefinedAs & \rsem{A} \rho \relSum \rsem{B} \rho \\
  \rsem{\forall i\mathord:s.A} \rho & \isDefinedAs & 
  \bigcap\{ \rsem{A} {(\rho,m)} \sepbar m \in \semSort{s} \} \\
  \rsem{\exists i\mathord:s.A} \rho & \isDefinedAs & 
  \bigcup\{ \rsem{A} {(\rho,m)} \sepbar m \in \semSort{s} \}
\end{eqnarray*}
In this definition, the relational interpretation of an application of
a primitive type $\rsem{\tyPrim{X}{e_1,\ldots,e_n}}\rho$ is built from
the relational interpretation of the primitive type,
$\rsem{\tyPrimNm{X}}$, and the interpretation of the index terms
$e_1,...,e_n$ in the index environment $\rho$. Universal and
existential quantification are interpretated by the set-theoretic
intersection and union, respectively, over all extensions of the index
environment.

>>>>

\paragraph{Relational interpretation of types.}
We assign a relational interpretation to all well-indexed types $\Delta
\vdash A \isType$ by induction on their derivations, parameterised by
index environments 
$\rho \in \semSort{\Delta}$:
\begin{eqnarray*}
%  \rsem{\Delta \vdash A \isType}M R & : & \semSort\Delta  \to \Rel(\tyPrimSem{A})\\
  \rsem{\tyUnit} \rho & \isDefinedAs & \{(*,*)\} \\
  \rsem{\tyPrim{X}{e_1,\ldots,e_n}}\rho & \isDefinedAs & 
  \semPrimType{\tyPrimNm{X}} (\semIndexExp{e_1}\rho, \ldots,
  \semIndexExp{e_n}\rho)\\
  \rsem{A \tyArr B} \rho & \isDefinedAs & \rsem{A}\rho \relArrow \rsem{B} \rho \\
  \rsem{A \tyProduct B}\rho & \isDefinedAs & \rsem{A} \rho \relTimes \rsem{B} \rho \\
  \rsem{A + B} \rho & \isDefinedAs & \rsem{A} \rho \relSum \rsem{B} \rho \\
  \rsem{\forall i\mathord:s.A} \rho & \isDefinedAs & 
  \bigcap\{ \rsem{A} {(\rho,m)} \sepbar m \in \semSort{s} \} \\
  \rsem{\exists i\mathord:s.A} \rho & \isDefinedAs & 
  \bigcup\{ \rsem{A} {(\rho,m)} \sepbar m \in \semSort{s} \}
\end{eqnarray*}
In this definition, the relational interpretation of an application of
a primitive type $\rsem{\tyPrim{X}{e_1,\ldots,e_n}}\rho$ is built from
the relational interpretation of the primitive type,
$\rsem{\tyPrimNm{X}}$, and the interpretation of the index terms
$e_1,...,e_n$ in the index environment $\rho$. Universal and
existential quantification are interpreted by the set-theoretic
intersection and union, respectively, over all extensions of the index
environment.
